Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
Excuse the cost model

The final query execution is designed to be entirely cost-based,
i.e. many alternative plans are generated, but the decision on whether
to use a certain plan is entirely up to the cost model. While the
framework is flexible and could support further research into cost
models, I have considered this to be future work, and only a small
heuristic cost model is present in the current system.

However, since the combination of remotely executed SPARQL with a
local cache and TPF is rather complex, the cost
heuristics are fairly elaborate. Moreover, since the objective of the
study is to take load off of the remote endpoint, the heuristics are
intended to make the proxy work harder than the remote endpoint.

>>>>

The final query execution is designed to be entirely cost-based,
i.e. many alternative plans are generated, but the decision on whether
to use a certain plan is entirely up to the cost model. While the
framework is flexible and could support further research into cost
models, I have considered this to be future work, and only a small
heuristic cost model is present in the current system. This is guided
by intuition and verified mainly by a number of tests in the code for
expected corner cases. Importantly the different parts of the cost
model are tuned to balance each other, not actually estimate the cost
of any actual operation.

Admittedly, with this approach, using the term ``cost model'' is
somewhat of a misnomer. An important motivation for this work is to
relieve the remote endpoint of stress, and so a principled approach
could attempt to estimate the cost for the remote endpoint, but
rather, the intuition explained in Section~\ref{sec:understandquery}
motivates the choices made in the following.

Moreover, since the combination of remotely executed SPARQL with a
local cache and TPF is rather complex, the cost heuristics are fairly
elaborate. Therefore, an attempt to create a proper cost model would
make that a primary focus of the research, rather than the empirical
analysis of a first-generation caching proxy integrating SPARQL and
LDF we set out to achieve. That being said, I have chosen to keep the
``cost model'' terminology since the usage of the metric resembles how
it is used in the literature.
